---
title: "index"
format: html
---

## Project Description

The analysis aims to evaluate the accuracy and stability of the drone’s sensors (accelerometer, gyroscope, and magnetometer), assess flight dynamics under various simulated conditions, and improve sensor calibration and fusion algorithms. It also seeks to refine flight control performance and develop machine learning models to enhance data accuracy and compensate for limitations in smartphone-based IMUs.
```{r}
library(tidyverse)

read_csv(here::here("data/raw/imu.csv"))

imu <- read_csv(here::here("data/raw/imu.csv"))
```


```{r}
# 2. CLEAN & PREPARE DATA
imu_clean <- imu %>%
  # Rename columns to clean, analysis-friendly names
  rename(
    time_ns = `time [ns]`,
    ax = `ax [m s-2]`,
    ay = `ay [m s-2]`,
    az = `az [m s-2]`,
    p  = `p [rad/s]`,
    q  = `q [rad/s]`,
    r  = `r [rad/s]`
  ) %>%
  
  # Select variables you want to keep
  select(time_ns, ax, ay, az, p, q, r) %>%
  
  # Remove missing values
  drop_na() %>%
  
  # Create useful new variables
  mutate(
    # Convert time from nanoseconds to seconds
    time_s = time_ns / 1e9,
    
    # Magnitude of total acceleration
    accel_total = sqrt(ax^2 + ay^2 + az^2),
    
    # Magnitude of total angular velocity
    gyro_total  = sqrt(p^2 + q^2 + r^2)
  )

```
```{r}
# 3. OUTPUT CLEANED DATA
imu_clean
write_csv(imu_clean,
          here::here("data/my-processed-data.csv"))

```

  





